### 2023-01-11 README.Rmd
Updates and cleaning; prep for submission

# `{clarify}`: Simulation-Based Inference for Regression Models

@@

`{clarify}` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.

@@

You can install the development version of `{clarify}` from [GitHub](https://github.com/) with:

@@

Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters. The delta method involves multiple assumptions: 1) the regression coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance. When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate. Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference; however, it is computationally intensive since the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.

@@

The `{clarify}` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `{clarify}` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; and `sim_setx()` computes predicted values at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`.

@@

`{clarify}` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing. We can compute the log marginal risk ratio below:

@@

```{r}
# Marginal risk ratio ATT, delta method-based
marginaleffects::comparisons(fit, variables = list(treat = 0:1),
                             newdata = subset(lalonde, treat == 1),
                             transform_pre = "lnratioavg") |>
  summary()
```

@@

We can also use `{clarify}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:

@@

`{clarify}` offers parallel processing for all estimation functions to speed up computation.

>>>>

# `clarify`: Simulation-Based Inference for Regression Models

@@

`clarify` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects. See the `clarify` [website](https://ngreifer.github.io/clarify) for documentation and other examples.

@@

You can install the development version of `clarify` from [GitHub](https://github.com/ngreifer/clarify) with:

@@

Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters. The delta method involves multiple assumptions: 1) the regression coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance. When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate. Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference; however, it is computationally intensive because the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.

@@

The `clarify` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predicted values at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()`  computes average dose-response functions. `clarify` also offers support for models fit to multiply imputed data with the `misim()` function.

@@

`clarify` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing. We can compute the log marginal risk ratio below:

@@

```{r}
# Marginal risk ratio ATT, delta method-based
marginaleffects::comparisons(fit, variables = "treat",
                             newdata = subset(lalonde, treat == 1),
                             transform_pre = "lnratioavg") |>
  summary()
```

@@

We can also use `clarify` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:

@@

`clarify` offers parallel processing for all estimation functions to speed up computation.
